「赴尘杯」2025 年普通高中学业水平选择性考试适应性演练

### 2025-01-19 Dustbound/English/Dustbound_English_I/paper.tex
fix: :pencil2: 修复了一处括号全半角不匹配问题
feat: 添加 B 篇阅读

{\bfseries 第一节（共 15 小题；每小题 2.5 分，满分 37.5 分)}
\end{flushleft}

@@

>>>>

{\bfseries 第一节（共 15 小题；每小题 2.5 分，满分 37.5 分）}
\end{flushleft}

@@

\needspace{4\baselineskip}
{\centering \bfseries B \par}

{\centering \bfseries Passerine / Dream SMP Fanwork - Chapter 1 \par}

“You’re a bastard,” Techno said playfully, even as the voices screamed, run, run, run. He took Philza’s offered hand and pulled himself up beside the man that he was sure could have cut him in two, no matter how dulled the sword’s edge was. As Philza patiently moved Techno through all the things he’d done wrong (small things like foot placement and his hilt grip being an inch off), Techno found it equal parts amusing and frightening that despite his eons of bloody fighting, it took only a few minutes of sparring for Philza to find flaws in his technique. But then again, Techno’s technique wasn’t particularly polished; it took only one brutal swing to fell most people. Something told him that Philza would be harder to kill than that.

They conquered nations, he and his golden-haired friend. They were bathed in glory, twin gods shining in the middle of a bloody fields. But as their empire grew, so did their enemies. They came in droves, day after day, and before long Techno had forgotten what peace tasted like. The days were long and the nights were longer; every flicker of movement was a spy in the shadows, every ally was a potential traitor, every word was a declaration of war. Their home had become a target for a thousand armies.

Through it all, his one constant was Philza—until he wasn’t. Technoblade simply looked up one day from a map detailing enemy lines and realized he’d been talking to empty air. He had no idea how long he’d been alone, sitting in a dusty library with stale tea untouched in the corner. He had no idea if Philza ever said he was leaving, or if he simply went as he arrived suddenly, swiftly, like a snowstorm.

Afterwards, there was hardly any point in maintaining the empire. The voices were getting bored, anyway. They wanted more. A fresh fight, more stories. So Techno took his sword and his shield, and abandoned ship. He’d done it a million times before, but the thought of a chess board lying unused in a crumbling castle made him feeling something close to regret.

Technoblade wandered the world, trying to appease the voices. Neither of them were ever satisfied. No matter how much chaos he dealt, there was always more work to be done. So he worked. He had no idea for how long. All he remembered from that bloody time was a sense of unfulfillment, like a story had been left unfinished halfway through. Years. Decades. Maybe more. It hardly mattered.

In the end, he knew, it would all be the same. The world would end, and he would remain—always fighting, always alone. He’d seen it in his dreams, in the visions that plagued him. The world would end, and he would remain.

\needspace{4\baselineskip}
\begin{question}
What is the relationship between Technoblade and Philza in the story?
\begin{choices}
  \item They are twin gods who have conquered nations and are bathed in glory.
  \item They are friends who have fought side by side and have grown apart over time.
  \item They are enemies who have fought each other for eons and have never been able to kill each other.
  \item They are allies who have been betrayed by their enemies and have been forced to abandon their empire.
\end{choices}
\end{question}

\needspace{4\baselineskip}
\begin{question}
What is the main reason for Technoblade to abandon his empire and wander the world?
\begin{choices}
  \item He was bored with the empire and wanted to find new challenges.
  \item He was betrayed by his allies and was forced to leave the empire.
  \item He was haunted by the voices in his head and was unable to find peace.
  \item He was tired of fighting and wanted
\end{choices}
\end{question}

\needspace{4\baselineskip}
\begin{question}
What is the author's attitude towards the relationship between Technoblade and Philza?
\begin{choices}
  \item Neutral.
  \item Sympathetic.
  \item Critical.
  \item Humorous.
\end{choices}
\end{question}

\needspace{4\baselineskip}
\begin{question}
What is the main theme of the story?
\begin{choices}
  \item The importance of friendship and loyalty.
  \item The inevitability of conflict and betrayal.
  \item The futility of power and glory.
  \item The loneliness of eternal existence.
\end{choices}
\end{question}
